---
title: '695'
author: "Mengtian Guo"
date: "August 3, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
### Data Description
```{r, echo=FALSE}
x=5
````
Inline code will be included here `x=5`.

*italized*
**bold**



# "Income" dataset exercise

## Research question
I wanted to find out whether and how occupation and industry predict pay. The hypotheses is that occupation and industry predict pay.

## Data cleaning
```{r, echo=FALSE}
d=read.csv("C:/Users/Nicole Guo/Downloads/income.csv")

d=na.omit(d)
str(d)
```


## Analysis
I will run three multiple regressions, on all pay, male pay, and female pay.
```{r}
d$Occupation=as.numeric(d$Occupation)
d$Industry=as.numeric(d$Industry)
str(d)

Allresults=lm(All_workers~Occupation+Industry, data=d)
summary(Allresults)

Mresults=lm(M_workers~Occupation+Industry, data=d)
summary(Mresults)

Fresults=lm(F_workers~Occupation+Industry, data=d)
summary(Fresults)
```

## Evaluation
As the p-value is larger than 0.05 for both variables in all three models, I conclude that neither occupation or industry predicts pay, in none of the following models: all, male-only and female-only.

## Conclusion
None of the models/hypotheses is good.